Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-28 publication/manuscript.Rmd
update availability of data section
update code availability section

### Availability of Data and Material
\url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}

### Code Availability
\url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}

>>>>

### Code Availability
All analysis code is available from \url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}

### Availability of Data
Our analysis code downloads all benchmark datasets from \url{https://www.openml.org/}.
